---
title: "Lab 5: Point Estimates and Interval Estimates"
author: "Madeline Craft"
date: "2/15/2019"
output: html_document
---

Let's start by reading in our data. 

```{r}
setwd("/Users/madelinecraft/Desktop/103A Winter 2019/Week 1 Lab")
getwd()
mydata<-read.csv("edu_data.csv")
head(mydata)
```

###Point Estimate of a Sample Proportion

$$\hat{p} = \frac {x}{n}$$

We are going to use the following code to calculate the proportion of people in this sample who go to school year round.

```{r}
frequencies <- table(mydata$yr_rnd)
denominator <- sum(frequencies)
denominator
numerator <- frequencies[2]
numerator
proportion <- numerator/denominator 
proportion
```

###Point Estimate of a Sample Mean

$$\bar{x} = \frac {\sum x_{i}}{n}$$

```{r}
mean(mydata$meals)
```

###Interval Estimate for a Sample Proportion

$$\hat{p} \pm crit.value * \sqrt \frac {\hat{p}*(1-\hat{p})}{n}$$

The standard error of $\hat{p}$ is $\sqrt \frac {\hat{p}*(1-\hat{p})}{n}$ and the margin of error is $crit.value * \sqrt \frac {\hat{p}*(1-\hat{p})}{n}$. So, rather than calculating the interval estimate by hand, let's use the following function to calculate it for us!

```{r}
?prop.test
prop.test(90, 315, alternative = c("two.sided"), conf.level = 0.95)
prop.test(90, 315, alternative = c("greater"), conf.level = 0.95)
prop.test(90, 315, alternative = c("less"), conf.level = 0.95)
```

###Interval Estimate for a Sample Mean

$$\bar{x} \pm crit.val * \sqrt \frac {\sigma^2}{n}$$

What is the point estimate?  
What is the margin of error?  
What is the standard error of the point estimate?

Rather than calculating the interval estimate by hand, let's use the following function to calculate it for us!

```{r}
?t.test
t.test(mydata$meals, conf.level = 0.95)
```